---
title: "Binary Response"
---

```{r}
#| echo: false
#| message: false
#| warning: false
#| cache: true
#| results: markup

library(tidyverse)

data.clean <- read_csv("data/DataCleaningR.csv")

data.filter <- data.clean %>%
  drop_na() %>%
  mutate(FilterMinAppear_F = factor(FilterMinAppear)) %>%
  rename(Sensitivity = Recall) %>%
  filter(EmbeddingMethod != "BagOfWords", EmbeddingMethod != "TF-IDF") %>%
  mutate(ClassificationMethod = str_replace_all(ClassificationMethod, pattern = "LogisticRegression", replacement = "LogReg")) %>%
  mutate(ClassificationMethod = factor(ClassificationMethod, levels = c("LDA","QDA","MDA","FDA","LogReg","Tree","RF")), EmbeddingMethod = factor(EmbeddingMethod, levels = c("CBoW100","CBoW200","CBoW300","CBoW768","SG100","SG200","SG300","SG768","GloVe100","GloVe200","GloVe300","GloVe768","BERT","PCA")))

colrs.emb <- c("#12694f","#188c69","#21c090","#3fdeaf", "#645fab","#7570b3","#9794c7","#bebcdc","#b65002","#d95f02","#fd750d","#fd8c35","#e7298a","#66a61e")
colrs.class <- c("#2a618d","#3881bc","#72a8d5","#91bbde","#e41a1c","#4daf4a","#327330")
shap.emb <- c(2, 6, 14, 17, 1, 10, 13, 16,3, 5, 0, 7, 12, 15)
shap.class <- c(15, 0, 7, 12, 1, 2, 6)
lt <- c(1,2,3,4,5,6,1,2,3,4,5,6,1,2)
ltc <- c(1,2,3,4,5,6,1)
```

**I WILL COME BACK AND ADD FIGURE CAPTIONS TO ALL FIGURES LATER**

**ALSO NEED TO ADD TITLES TO ALL GRAPHS (MAYBE NOT NECESSARY IF ADD CAPTIONS... NEED TO THINK ABOUT)**

# Accuracy

### Classification \* Embedding \* Stopwords

```{r}
#| echo: false
#| message: false
#| warning: false
#| tidy: true
#| cache: true
#| fig-height: 10
#| fig-width: 10

CES <- data.filter %>% group_by(ClassificationMethod,EmbeddingMethod,FilterStopwords) %>% 
  select(ClassificationMethod, EmbeddingMethod, FilterStopwords, Accuracy)
CES.no <- CES %>% subset(FilterStopwords == "No")
CES.yes <- CES %>% subset(FilterStopwords == "Yes")
CES.no$CES.acc.yes <- CES.yes$Accuracy
CES.new <- CES.no %>% summarize(CES.diff = Accuracy - CES.acc.yes)

CES.new %>% 
  ggplot(aes(x = ClassificationMethod, y = CES.diff, fill = ClassificationMethod)) +
  geom_violin(trim=FALSE, position = position_dodge(1))  +
  stat_summary(fun = mean, geom = "point", shape = 16, size = 2, color = '#E2DFDF') +
  stat_summary(fun = median, geom = "point", shape = 17, size = 2) +
  facet_wrap(~EmbeddingMethod,ncol = 4)+
  geom_hline(yintercept = 0, linetype = 'dashed', linewidth =1)+
  scale_fill_manual(values = colrs.class)+
  xlab("Classification Method") +
  ylab("Difference in Accuracy Rates")+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),legend.position = "none")
```

### Classification \* Stopwords

```{r}
#| echo: false
#| message: false
#| warning: false
#| tidy: true
#| cache: true
#| fig-height: 10
#| fig-width: 5


data.filter %>% ggplot(aes(x = FilterStopwords, y = Accuracy, fill = FilterStopwords)) +
  geom_violin(trim=FALSE, position = position_dodge(1))  +
  stat_summary(fun = mean, geom = "point", shape = 16, size = 2, color = '#E2DFDF') +
  stat_summary(fun = median, geom = "point", shape = 17, size = 2) +
  facet_wrap(~ClassificationMethod,ncol=2)+
  geom_hline(yintercept = 0.5, linetype = 'dashed', size =1)+
  xlab("Filter Stopwords?") +
  ylab("Accuracy Rate")+
  theme_bw()+
  theme(legend.position = "none")
```

### Embedding \* Stopwords

```{r}
#| echo: false
#| message: false
#| warning: false
#| tidy: true
#| cache: true
#| fig-height: 10
#| fig-width: 10

data.filter %>% 
  ggplot(aes(x = FilterStopwords, y = Accuracy, fill = FilterStopwords)) +
  geom_violin(trim=FALSE, position = position_dodge(1))  +
  stat_summary(fun = mean, geom = "point", shape = 16, size = 2, color = '#E2DFDF') +
  stat_summary(fun = median, geom = "point", shape = 17, size = 2) +
  facet_wrap(~EmbeddingMethod,ncol = 4)+
  geom_hline(yintercept = 0.5, linetype = 'dashed', linewidth =1)+
  xlab("Filter Stopwords?") +
  ylab("Accuracy Rate")+
  theme_bw()+
  theme(legend.position = "none")

```

### Classification \* Minimum Number of Appearances

```{r}
#| echo: false
#| message: false
#| warning: false
#| tidy: true
#| cache: true
#| fig-height: 10
#| fig-width: 5


data.filter %>% ggplot(aes(x = FilterMinAppear_F, y = Accuracy, fill = FilterMinAppear_F)) +
  geom_violin(trim=FALSE, position = position_dodge(1))  +
  stat_summary(fun = mean, geom = "point", shape = 16, size = 2, color = '#E2DFDF') +
  stat_summary(fun = median, geom = "point", shape = 17, size = 2) +
  facet_wrap(~ClassificationMethod,ncol = 2)+
  geom_hline(yintercept = 0.5, linetype = 'dashed', size =1)+
  xlab("Minimum Number of Appearances") +
  ylab("Accuracy Rate")+
  theme_bw()+
  theme(legend.position = "none")
```

### Embedding \* Minimum Number of Appearances

```{r}
#| echo: false
#| message: false
#| warning: false
#| tidy: true
#| cache: true
#| fig-height: 10
#| fig-width: 10


data.filter %>% 
  ggplot(aes(x = FilterMinAppear_F, y = Accuracy, fill = FilterMinAppear_F)) +
  geom_violin(trim=FALSE, position = position_dodge(1))  +
  stat_summary(fun = mean, geom = "point", shape = 16, size = 2, color = '#E2DFDF') +
  stat_summary(fun = median, geom = "point", shape = 17, size = 2) +
  facet_wrap(~EmbeddingMethod,ncol = 4)+
  geom_hline(yintercept = 0.5, linetype = 'dashed', size =1)+
  xlab("Minimum Number of Appearances") +
  ylab("Accuracy Rate")+
  theme_bw()+
  theme(legend.position = "none")
```

### Classification \* Embedding

```{r}
#| echo: false
#| message: false
#| warning: false
#| tidy: true
#| cache: true
#| fig-height: 10
#| fig-width: 10

data.filter %>% 
  ggplot(aes(x = ClassificationMethod, y = Accuracy, fill = ClassificationMethod)) +
  geom_violin(trim=FALSE, position = position_dodge(1))  +
  facet_wrap(~EmbeddingMethod, ncol=4)+
  geom_hline(yintercept = 0.5, linetype = 'dashed', size =1)+
  stat_summary(fun = mean, geom = "point", shape = 16, size = 2, color = '#E2DFDF') +
  stat_summary(fun = median, geom = "point", shape = 17, size = 2) +
  scale_fill_manual(values = colrs.class) +
  xlab("Classification Method") +
  ylab("Accuracy Rate")+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), legend.position = "none")
```

### Classification

```{r}
#| echo: false
#| message: false
#| warning: false
#| tidy: true
#| cache: true

data.filter %>% 
  ggplot(aes(x = ClassificationMethod, y = Accuracy, fill = ClassificationMethod)) +
   geom_violin(trim=FALSE) +
   stat_summary(fun = mean, geom = "point", shape = 16, size = 2, color = '#E2DFDF') +
  stat_summary(fun = median, geom = "point", shape = 17, size = 2) +
  geom_hline(yintercept = 0.5, linetype = 'dashed', size =1)+
  scale_fill_manual(values = colrs.class)+
  theme_bw()+
  theme(legend.position = "none") +
  xlab("Classification Method") +
  ylab("Accuracy Rate")
```

### Embedding

```{r}
#| echo: false
#| message: false
#| warning: false
#| tidy: true
#| cache: true

data.filter %>% ggplot(aes(x = EmbeddingMethod, y = Accuracy, fill = EmbeddingMethod)) +
   geom_violin(trim=FALSE) +
   stat_summary(fun = mean, geom = "point", shape = 16, size = 2, color = '#E2DFDF') +
  stat_summary(fun = median, geom = "point", shape = 17, size = 2) +
  geom_hline(yintercept = 0.5, linetype = 'dashed', size =1)+
  scale_fill_manual(values = colrs.emb)+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), legend.position = "none")+
  xlab("Embedding Method") +
  ylab("Accuracy Rate")
```

### Stop words

```{r}
#| echo: false
#| message: false
#| warning: false
#| tidy: true
#| cache: true

data.filter %>% ggplot(aes(x = FilterStopwords, y = Accuracy, fill = FilterStopwords)) +
  geom_violin(trim=FALSE) +
   stat_summary(fun = mean, geom = "point", shape = 16, size = 2, color = '#E2DFDF') +
  stat_summary(fun = median, geom = "point", shape = 17, size = 2) +
  geom_hline(yintercept = 0.5, linetype = 'dashed', size =1)+
  theme_bw()+
  theme(legend.position = "none")+
  xlab("Filtering Stop Words?") +
  ylab("Accuracy Rate")
```

### Minimum number of appearances

```{r}
#| echo: false
#| message: false
#| warning: false
#| tidy: true
#| cache: true

data.filter %>% ggplot(aes(x = FilterMinAppear_F, y = Accuracy, fill = FilterMinAppear_F)) +
  geom_violin(trim=FALSE) +
  stat_summary(fun = mean, geom = "point", shape = 16, size = 2, color = '#E2DFDF') +
  stat_summary(fun = median, geom = "point", shape = 17, size = 2) +
  geom_hline(yintercept = 0.5, linetype = 'dashed', size =1)+
  theme_bw()+
  theme(legend.position = "none")+
  xlab("Minimum Number of Appearances") +
  ylab("Accuracy Rate")
```

### Numbers

```{r}
#| echo: false
#| message: false
#| warning: false
#| tidy: true
#| cache: true

data.filter %>% ggplot(aes(x = FilterNumbers, y = Accuracy, fill = FilterNumbers)) +
  geom_violin(trim=FALSE) +
  stat_summary(fun = mean, geom = "point", shape = 16, size = 2, color = '#E2DFDF') +
  stat_summary(fun = median, geom = "point", shape = 17, size = 2) +
  geom_hline(yintercept = 0.5, linetype = 'dashed', size =1)+
  xlab("Filter Numbers?") +
  ylab("Accuracy Rate")+
  theme_bw()+
  theme(legend.position = "none")
```

# Precision

### Classification \* Embedding \* Min Appearances

```{r}
#| echo: false
#| message: false
#| warning: false
#| tidy: true
#| cache: true
#| fig-height: 10
#| fig-width: 10

CEF.prec <- data.filter %>% group_by(ClassificationMethod,EmbeddingMethod,FilterMinAppear_F) %>% 
  summarize(CEF.means = mean(Precision))

CEF.prec$ClassificationMethod <- gsub("LogReg", "G", CEF.prec$ClassificationMethod)
CEF.prec$ClassificationMethod <- gsub("LDA", "L", CEF.prec$ClassificationMethod)
CEF.prec$ClassificationMethod <- gsub("QDA", "Q", CEF.prec$ClassificationMethod)
CEF.prec$ClassificationMethod <- gsub("MDA", "M", CEF.prec$ClassificationMethod)
CEF.prec$ClassificationMethod <- gsub("FDA", "F", CEF.prec$ClassificationMethod)
CEF.prec$ClassificationMethod <- gsub("Tree", "T", CEF.prec$ClassificationMethod)
CEF.prec$ClassificationMethod <- gsub("RF", "R", CEF.prec$ClassificationMethod)
CEF.prec$ClassificationMethod <- factor(CEF.prec$ClassificationMethod, levels = c("L","Q","M","F","G","T","R"))

CEF.prec %>% ggplot() + aes(x = EmbeddingMethod, y=CEF.means, color = ClassificationMethod) + 
  geom_text(aes(label = ClassificationMethod)) +
  facet_wrap(~FilterMinAppear_F, ncol = 2)+
  geom_hline(yintercept = 0.5, linetype = 'dashed', size =1)+
  scale_color_manual(values = colrs.class)+
  xlab("Embedding Method") +
  ylab("Precision Rate")+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), legend.position = "none")
```

### Classification \* Embedding \* Stopwords

```{r}
#| echo: false
#| message: false
#| warning: false
#| tidy: true
#| cache: true
#| fig-height: 10
#| fig-width: 10

CES.prec <- data.filter %>% group_by(ClassificationMethod,EmbeddingMethod,FilterStopwords) %>% 
  select(ClassificationMethod, EmbeddingMethod, FilterStopwords, Precision)
CES.prec.no <- CES.prec %>% subset(FilterStopwords == "No")
CES.prec.yes <- CES.prec %>% subset(FilterStopwords == "Yes")
CES.prec.no$CES.prec.yes <- CES.prec.yes$Precision
CES.prec.new <- CES.prec.no %>% summarize(CES.diff = Precision - CES.prec.yes)

CES.prec.new %>% 
  ggplot(aes(x = ClassificationMethod, y = CES.diff, fill = ClassificationMethod)) +
  geom_violin(trim=FALSE, position = position_dodge(1))  +
  stat_summary(fun = mean, geom = "point", shape = 16, size = 2, color = '#E2DFDF') +
  stat_summary(fun = median, geom = "point", shape = 17, size = 2) +
  facet_wrap(~EmbeddingMethod,ncol = 4)+
  geom_hline(yintercept = 0, linetype = 'dashed', linewidth =1)+
  scale_fill_manual(values = colrs.class)+
  xlab("Classification Method") +
  ylab("Precision Rate")+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),legend.position = "none")
```

### Classification \* Stopwords

```{r}
#| echo: false
#| message: false
#| warning: false
#| tidy: true
#| cache: true
#| fig-height: 10
#| fig-width: 5

data.filter %>% ggplot(aes(x = FilterStopwords, y = Precision, fill = FilterStopwords)) +
  geom_violin(trim=FALSE, position = position_dodge(1))  +
  stat_summary(fun = mean, geom = "point", shape = 16, size = 2, color = '#E2DFDF') +
  stat_summary(fun = median, geom = "point", shape = 17, size = 2) +
  facet_wrap(~ClassificationMethod, ncol=2)+
  geom_hline(yintercept = 0.5, linetype = 'dashed', size =1)+
  xlab("Filter Stop Words?") +
  ylab("Precision Rate")+
  theme_bw()+
  theme(legend.position = "none")

```

### Embedding \* Stopwords

```{r}
#| echo: false
#| message: false
#| warning: false
#| tidy: true
#| cache: true
#| fig-height: 10
#| fig-width: 10

data.filter %>%
  ggplot(aes(x = FilterStopwords, y = Precision, fill = FilterStopwords)) +
  geom_violin(trim=FALSE, position = position_dodge(1))  +
  stat_summary(fun = mean, geom = "point", shape = 16, size = 2, color = '#E2DFDF') +
  stat_summary(fun = median, geom = "point", shape = 17, size = 2) +
  facet_wrap(~EmbeddingMethod, ncol=4)+
  geom_hline(yintercept = 0.5, linetype = 'dashed', size =1)+
  xlab("Filter Stop Words?") +
  ylab("Precision Rate")+
  theme_bw()+
  theme(legend.position = "none")

```

### Classification \* Numbers

```{r}
#| echo: false
#| message: false
#| warning: false
#| tidy: true
#| cache: true
#| fig-height: 10
#| fig-width: 5

data.filter %>% ggplot(aes(x = FilterNumbers, y = Precision, fill = FilterNumbers)) +
  geom_violin(trim=FALSE, position = position_dodge(1))  +
  stat_summary(fun = mean, geom = "point", shape = 16, size = 2, color = '#E2DFDF') +
  stat_summary(fun = median, geom = "point", shape = 17, size = 2) +
  facet_wrap(~ClassificationMethod, ncol=2)+
  geom_hline(yintercept = 0.5, linetype = 'dashed', size =1)+
  xlab("Filter Numbers?") +
  ylab("Precision Rate")+
  theme_bw()+
  theme(legend.position = "none")

```

### Embedding \* Numbers

```{r}
#| echo: false
#| message: false
#| warning: false
#| tidy: true
#| cache: true
#| fig-height: 10
#| fig-width: 10

data.filter %>%
  ggplot(aes(x = FilterNumbers, y = Precision, fill = FilterNumbers)) +
  geom_violin(trim=FALSE, position = position_dodge(1))  +
  stat_summary(fun = mean, geom = "point", shape = 16, size = 2, color = '#E2DFDF') +
  stat_summary(fun = median, geom = "point", shape = 17, size = 2) +
  facet_wrap(~EmbeddingMethod, ncol=4)+
  geom_hline(yintercept = 0.5, linetype = 'dashed', size =1)+
  xlab("Filter Numbers?") +
  ylab("Precision Rate")+
  theme_bw()+
  theme(legend.position = "none") 
```

### Classification \* Minimum

```{r}
#| echo: false
#| message: false
#| warning: false
#| tidy: true
#| cache: true
#| fig-height: 10
#| fig-width: 5

data.filter %>% ggplot(aes(x = FilterMinAppear_F, y = Precision, fill = FilterMinAppear_F)) +
  geom_violin(trim=FALSE, position = position_dodge(1))  +
  stat_summary(fun = mean, geom = "point", shape = 16, size = 2, color = '#E2DFDF') +
  stat_summary(fun = median, geom = "point", shape = 17, size = 2) +
  facet_wrap(~ClassificationMethod,ncol = 2)+
  geom_hline(yintercept = 0.5, linetype = 'dashed', size =1)+
  xlab("Minimum Number of Appearances") +
  ylab("Precision Rate")+
  theme_bw()+
  theme(legend.position = "none")
```

### Embedding \* Minimum

```{r}
#| echo: false
#| message: false
#| warning: false
#| tidy: true
#| cache: true
#| fig-height: 10
#| fig-width: 10

data.filter %>%
  ggplot(aes(x = FilterMinAppear_F, y = Precision, fill = FilterMinAppear_F)) +
  geom_violin(trim=FALSE, position = position_dodge(1))  +
  stat_summary(fun = mean, geom = "point", shape = 16, size = 2, color = '#E2DFDF') +
  stat_summary(fun = median, geom = "point", shape = 17, size = 2) +
  facet_wrap(~EmbeddingMethod,ncol = 4)+
  geom_hline(yintercept = 0.5, linetype = 'dashed', size =1)+
  xlab("Minimum Number of Appearances") +
  ylab("Precision Rate")+
  theme_bw()+
  theme(legend.position = "none") 
```

### Classification \* Embedding

```{r}
#| echo: false
#| message: false
#| warning: false
#| tidy: true
#| cache: true
#| fig-height: 10
#| fig-width: 10

data.filter %>% 
  ggplot(aes(x = ClassificationMethod, y = Precision, fill = ClassificationMethod)) +
  geom_violin(trim=FALSE, position = position_dodge(1))  +
  stat_summary(fun = mean, geom = "point", shape = 16, size = 2, color = '#E2DFDF') +
  stat_summary(fun = median, geom = "point", shape = 17, size = 2) +
  facet_wrap(~EmbeddingMethod, ncol=4)+
  geom_hline(yintercept = 0.5, linetype = 'dashed', size =1)+
  scale_fill_manual(values = colrs.class) +
  xlab("Embedding Method") +
  ylab("Precision Rate")+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), legend.position = "none")
```

### Classification

```{r}
#| echo: false
#| message: false
#| warning: false
#| tidy: true
#| cache: true
#| fig-height: 10
#| fig-width: 10

data.filter %>% 
  ggplot(aes(x = ClassificationMethod, y = Precision, fill = ClassificationMethod)) +
   geom_violin(trim=FALSE) +
   stat_summary(fun = mean, geom = "point", shape = 16, size = 2, color = '#E2DFDF') +
  stat_summary(fun = median, geom = "point", shape = 17, size = 2) +
  geom_hline(yintercept = 0.5, linetype = 'dashed', size =1)+
  scale_fill_manual(values = colrs.class)+
  theme_bw()+
  theme(legend.position = "none") +
  xlab("Classification Method") +
  ylab("Precision Rate")
```

### Embedding

```{r}
#| echo: false
#| message: false
#| warning: false
#| tidy: true
#| cache: true
#| fig-height: 10
#| fig-width: 10

data.filter %>% ggplot(aes(x = EmbeddingMethod, y = Precision, fill = EmbeddingMethod)) +
   geom_violin(trim=FALSE) +
   stat_summary(fun = mean, geom = "point", shape = 16, size = 2, color = '#E2DFDF') +
  stat_summary(fun = median, geom = "point", shape = 17, size = 2) +
  geom_hline(yintercept = 0.5, linetype = 'dashed', size =1)+
  scale_fill_manual(values = colrs.emb)+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), legend.position = "none")+
  xlab("Embedding Method") +
  ylab("Precision Rate")
```

### Stopwords

```{r}
#| echo: false
#| message: false
#| warning: false
#| tidy: true
#| cache: true
#| fig-height: 10
#| fig-width: 10

data.filter %>% ggplot(aes(x = FilterStopwords, y = Precision, fill = FilterStopwords)) +
  geom_violin(trim=FALSE) +
  stat_summary(fun = mean, geom = "point", shape = 16, size = 2, color = '#E2DFDF') +
  stat_summary(fun = median, geom = "point", shape = 17, size = 2) +
  geom_hline(yintercept = 0.5, linetype = 'dashed', size =1)+
  theme_bw()+
  theme(legend.position = "none") +
  xlab("Filter Stop Words?") +
  ylab("Precision Rate")
```

### Minimum

```{r}
#| echo: false
#| message: false
#| warning: false
#| tidy: true
#| cache: true
#| fig-height: 10
#| fig-width: 10

data.filter %>% ggplot(aes(x = FilterMinAppear_F, y = Precision, fill = FilterMinAppear_F)) +
  geom_violin(trim=FALSE) +
  stat_summary(fun = mean, geom = "point", shape = 16, size = 2, color = '#E2DFDF') +
  stat_summary(fun = median, geom = "point", shape = 17, size = 2) +
  geom_hline(yintercept = 0.5, linetype = 'dashed', size =1)+
  theme_bw()+
  theme(legend.position = "none") +
  xlab("Minimum Number of Appearances") +
  ylab("Precision Rate")
```

### Lowercase

```{r}
#| echo: false
#| message: false
#| warning: false
#| tidy: true
#| cache: true
#| fig-height: 10
#| fig-width: 10

data.filter %>% ggplot(aes(x = ConvertLower, y = Precision, fill = ConvertLower)) +
  geom_violin(trim=FALSE) +
  stat_summary(fun = mean, geom = "point", shape = 16, size = 2, color = '#E2DFDF') +
  stat_summary(fun = median, geom = "point", shape = 17, size = 2) +
  geom_hline(yintercept = 0.5, linetype = 'dashed', size =1)+
  theme_bw()+
  theme(legend.position = "none") +
  xlab("Convert Lower?") +
  ylab("Precision Rate")
```
